method

### 2022-02-17 06_Paper/ER-ED/method.Rmd
added variable block

library(targets)    # to keep track of all relevant files
library(readxl)     # import excel files
library(here)       # to set directories without defined paths
library(papaja)     # APA conform output
library(afex)       # for ANOVA
library(emmeans)
library(ggplot2)    # for nice plots
library(dplyr)
library(BayesFactor)
library(effectsize)

@@

>>>>

library(targets)    # to keep track of all relevant files
library(readxl)     # import excel files
library(here)       # to set directories without defined paths
library(papaja)     # APA conform output
library(afex)       # for ANOVA
library(emmeans)
library(ggplot2)    # for nice plots
library(dplyr)
library(BayesFactor)
library(effectsize)
library(dplyr)

@@

# create variable "block"

data_EMG$block[data_EMG$trigger == " S 21"] <- "view_neg"
data_EMG$block[data_EMG$trigger == " S 22"] <- "view_neg"
data_EMG$block[data_EMG$trigger == " S 23"] <- "distraction"
data_EMG$block[data_EMG$trigger == " S 24"] <- "distancing"
data_EMG$block[data_EMG$trigger == " S 25"] <- "suppression"
data_EMG$block[data_EMG$trigger == " S 26"] <- "choice"
